### 2018-03-03 analysis_code/tournament_table.Rmd
updates

```{r echo=FALSE,message=FALSE}

@@

dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/memory_experiment_raw_results_2.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
priors <- as.list(unique(dat['Prior']))$Prior
EXPERIMENT_1_CV_HIGH <- 156.71410383 #chisquared critical values for 124 degrees of freedom
EXPERIMENT_1_CV_LOW <- 95.07008897

@@

ZERO_ONE_CUTOFF <- 0.1
```

```{r echo=FALSE, xtable, results="asis"}
algs <- c("ThompsonSampling", "DynamicEpsilonGreedy", "DynamicGreedy")
options(xtable.sanitize.text.function=identity)
options(xtable.caption.placement="top")
library(xtable)
for (prior in priors) {
  for (i in 1:length(agent_algs)) {
    agent_alg <- agent_algs[i]
    for (j in 1:length(time_horizons)) {
      time <- time_horizons[j]
      results <- matrix(nrow=length(algs), ncol=length(algs))
      colnames(results) <- algs
      rownames(results) <- algs
      for (k in 1:length(algs)) {
        for (l in 1:length(algs)) {
          p1alg = algs[k]
          p2alg = algs[l]
          if (p1alg == p2alg) { next }
          filtered_dat <- filter(dat, P1.Alg == p1alg & P2.Alg == p2alg & Memory.Size == 100 & Prior == prior & Agent.Alg == agent_alg & Time.Horizon == time)
          if (nrow(filtered_dat) == 0) {
            next
          }
          share <- filtered_dat$Market.Share.for.P1
          test <- t.test(share)
          cin <- signif(test$conf.int[2] - mean(share), digits=4)
          shares <- sum(share >= (1 - ZERO_ONE_CUTOFF) | share <= ZERO_ONE_CUTOFF, na.rm=TRUE) / nrow(filtered_dat)
          lower_var <- signif((length(share) - 1) * var(share) / EXPERIMENT_1_CV_HIGH, digits=4)
          high_var <- signif((length(share) - 1) * var(share) / EXPERIMENT_1_CV_LOW, digits=4)
          results[k, l] <- paste("<b>",signif(mean(share), digits=4), "</b> +/-", cin, "<br>", signif(var(share), digits=4), paste("(", lower_var, ", ", high_var, ")", sep=""), "<br>", "Extreme Shares:", shares)
        }
      }
      tab <-xtable(results, caption=paste("Results for", agent_alg, time, prior))
      print(tab, type="html")
    }
    print('<br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br>')
  }
}

>>>>

```{r echo=FALSE,message=FALSE,xtable, results="asis"}

@@

dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_raw_results.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
priors <- as.list(unique(dat['Prior']))$Prior
EXPERIMENT_1_CV_HIGH <- 156.71410383 #chisquared critical values for 124 degrees of freedom
EXPERIMENT_1_CV_LOW <- 95.07008897

@@

ZERO_ONE_CUTOFF <- 0.1
algs <- c("ThompsonSampling", "DynamicEpsilonGreedy", "DynamicGreedy")
options(xtable.sanitize.text.function=identity)
options(xtable.caption.placement="top")
library(xtable)
for (prior in priors) {
  for (i in 1:length(agent_algs)) {
    agent_alg <- agent_algs[i]
    for (j in 1:length(time_horizons)) {
      time <- time_horizons[j]
      results <- matrix(nrow=length(algs), ncol=length(algs))
      colnames(results) <- algs
      rownames(results) <- algs
      for (k in 1:length(algs)) {
        for (l in 1:length(algs)) {
          p1alg = algs[k]
          p2alg = algs[l]
          filtered_dat <- filter(dat, P1.Alg == p1alg & P2.Alg == p2alg & Memory.Size == 100 & Prior == prior & Agent.Alg == agent_alg & Time.Horizon == time)
          if (nrow(filtered_dat) == 0) {
            next
          }
          share <- filtered_dat$Market.Share.for.P1
          test <- t.test(share)
          cin <- signif(test$conf.int[2] - mean(share), digits=4)
          shares <- sum(share >= (1 - ZERO_ONE_CUTOFF) | share <= ZERO_ONE_CUTOFF, na.rm=TRUE) / nrow(filtered_dat)
          lower_var <- signif((length(share) - 1) * var(share) / EXPERIMENT_1_CV_HIGH, digits=4)
          high_var <- signif((length(share) - 1) * var(share) / EXPERIMENT_1_CV_LOW, digits=4)
          results[k, l] <- paste("<b>",signif(mean(share), digits=4), "</b> +/-", cin, "<br>", signif(var(share), digits=4), paste("(", lower_var, ", ", high_var, ")", sep=""), "<br>", "Extreme Shares:", shares)
        }
      }
      tab <-xtable(results, caption=paste("Results for", agent_alg, time, prior))
      print(tab, type="html")
    }
    print('<br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br>')
  }
}
